Mentored data science research with tweets

### 2020-03-19 Rmd/introduction.Rmd
removed anonymous files

We elected to work with social media data. In making 
this decision, we recognized that social media data, such as tweets from 
Twitter, can be acquired with little cost and that there is growing research 
interest in social media in many social science disciplines, including political 
science, communication studies, and sociology. We also anticipated 
that our undergraduate trainees might be intrigued by the possibility of 
analyzing social media data, since many young adults use Facebook, Twitter, 
Instagram, and related sites.

>>>>

We elected to work with social media data. In making 
this decision, we recognized that social media data, such as tweets from 
Twitter, can be acquired with little cost and that there is growing research 
interest in social media in many social science disciplines, including political 
science, communication studies, public health, and sociology. We also anticipated 
that our undergraduate trainees might be intrigued by the possibility of 
analyzing social media data, since many young adults use Facebook, Twitter, 
Instagram, and related sites.

### 2020-03-19 Rmd/jse-2019-ms.Rmd
removed anonymous files

---
title: 'Backward designing a reproducible framework for undergraduate data science research'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: 
  bookdown::pdf_document2:
    includes:
      in_header: head.tex
---

Last modified: `r params$lastmod`

>>>>

---
title: 'Mentored data science research with tweets'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "May 15, 2020"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm"
output: 
  bookdown::pdf_book:
    toc: FALSE
    number_sections: TRUE
    includes:
      in_header: head.tex
---
